### 2016-09-02 notions.tex
OW notion returns
cleaning up privacy section

%\jnote{I don't know if I like the one-wayness definition any more; it seems a bit
%ad hoc. And why do we care about one-wayness, anyway? Instead, I give
%two versions of semantic security.}

%The one-wayness definition (see
%Figure~\ref{fig:privacy-ow}) is parameterized by a distribution $\distr{}{}$ over
%sets. A set $S$ is chosen from this distribution, and a representation
%$(\pubaux,\privaux)$ of that set is computed.
%In one experiment ($\ExpPriv{\Pi,\distr{}{}}$), an attacker~$A$ is given $\pubaux$;
%in a second experiment ($\ExpPrivNull{\Pi,\distr{}{}}{}$), it is not.
%For a given $\distr{}{}$ and $A$, we define the advantage measure
%$\AdvPriv{\Pi,\distr{}{}}{A} \bydef
%\left| \Prob{\ExpPriv{\Pi,\distr{}{}}{A}=1} - \Prob{\ExpPrivNull{\Pi,\distr{}{}}{P}=1} \right|$.
%We track the
%time-complexity~$t$ and number of oracle queries~$q$ made by the adversary.
%\jnote{Change. Compare $A$ in the 1-world to $P$ in the 0-world. Security means
%there exists a $P$
%such that for all~$A$ the following holds: $A$ in the 1-world does not do much better than
%$P$ in the 0-world. Note that there is a canonical $P$ that does best, information-theoretically.}
%\jnote{I now wonder whether we should allow test queries in both worlds.}
%
%\begin{figure}[hbtp]
%\centering
%\fpage{.6}{
%\hpagess{.5}{.45}
%{
%\experimentv{$\ExpPriv{\setprim,\distr{}{}}{A}$}\\
%$S \getsr \distr{}{}$\\
%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
%$z \getsr A^{\TestOracle}(M,\pubaux)$\\
%if $z \in S$ then return 1\\
%return 0\\
%
%\medskip
%\experimentv{$\ExpPrivNull{\Pi, \distr{}{}}{P}$} \\
%$S \getsr \distr{}{}$\\
%%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
%$z \getsr P()$\\
%if $z \in S$ then return 1\\
%return 0\\
%%\medskip
%%\experimentv{$\ExpWPriv{\setprim,\distr{}{}}{A}$}\\
%%$S \getsr \distr{}{}$\\
%%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
%%$z \getsr A^{\TestOracle}(\pubaux)$\\
%%if $z \in S$ then Return 1\\
%%Return 0\\
%}
%%
%{
%\oracle{$\TestOracle(q)$}\\
%$a \gets \Qry(M,\pubaux,\privaux,q)$\\
%return~$a$
%}
%}
%\caption{Experiments for a ``one-wayness'' style privacy
%  definition.}
%\label{fig:privacy-ow}
%\end{figure}

%\jnote{Actually, I am unsure whether a one-wayness definition is independently
%interesting if we have (and can achieve) a semantic-security definition.}
%\tsnote{Depends on what information we decide is okay to leak.  A
%  classical BF gives an~$M$ that leaks a good approximation of $|S|$.
%Do we want that to be considered semantically secure?  On the other
%hand, a classical BF is one-way in the ROM, up to the min-entropy of
%the distribution over~$S$.  So that may already give an interesting
%example that fits in the gap.} \jnote{Yes. Semantic security
%is parameterized by the leakage function, and so might or might not imply
%one-wayness.}
Our semantic-secure definition is simulation-based (see Figure~\ref{fig:privacy-ss}).
In this definition we compare the probabilities with which an attacker $A$ outputs~1
in two experiments: one ``real'' and one ``simulated.''
In the real experiment (ss-rep-1), $A$ outputs a set $S$  and is given the
public information $\pubaux$ that results from running $\Rep(S)$.
\footnote{We do not give $A$ an oracle for issuing queries; 
since $A$ knows the set~$S$, such an oracle would be superfluous.
\jnote{Interestingly,
if we provided a query oracle in the real world and an oracle that returns the correct
answer in the simulated world, then the definition seems to imply
correctness also.}}
In the simulated experiment (ss-rep-0), $A$ outputs $S$ and is given $\pubaux$ output
by a simulator $\Sim$ that is only given ${\sf leak}(S)$ for some (possibly randomized)
function~${\sf leak}$.
%\tsnote{Need to pass state between stages if you want~$A$ to know the
%  set it previously sampled, right?} \jnote{Yes, unless by convention all algorithms
%  are stateful. (smiley face). Whatever you prefer is fine with me.}
For a given function ${\sf leak}$, adversary $A$, and simulator~$\Sim$,
we define the advantage measure
$\AdvPrivSS{\Pi,{\sf leak}}{A,\Sim} \bydef
\left| \Prob{\ExpPrivSSreal{\Pi}{A}=1} -
\Prob{\ExpPrivSSsim{\Pi,{\sf leak}}{A, \Sim}=1} \right|$.
Informally, a scheme $\Pi$ is secure with respect to some leakage function ${\sf leak}$
if for all $A$ there is a simulator $\Sim$ such that
$\AdvPrivSS{\Pi,{\sf leak}}{A,\Sim}$ is small.
Intuitively, this means that the public portion
$\pubaux$ of the representation of a set~$S$ leaks~${\sf leak}(S)$ and nothing more.
\jnote{Need to relate running time of $\Sim$ to running time of~$A$.}

\begin{figure}[hbtp]
\centering
\fpage{.6}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpPrivSSreal{\Pi}{A}$}\\
$(S,\st) \getsr A()$ \\
$(\pubaux,\privaux) \getsr \Rep(S)$\\
return $A(\st,\pubaux)$\\
}
%
{
\experimentv{$\ExpPrivSSsim{\Pi, {\sf leak}}{A, \Sim}$}\\
$(S,\st) \getsr A()$\\
$(\st,\pubaux) \getsr \Sim({\sf leak}(S))$ \\
return $A(\st,\pubaux)$\\

%\medskip
%\experimentv{$\ExpPrivSSsim{\Pi}{A, \calS}$}\\
%$S \gets A()$\\
%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
%$(M',\pubaux) \gets \calS(\pubaux)$ \\
%return $A(M',\pubaux)$\\
}
}
\caption{Experiments for a ``semantic-security'' style privacy
  definition.}
\label{fig:privacy-ss}
\end{figure}

@@

\subsection{Relationships Among Notions}\todo{Decide which of these
  statements should have formal theorems and proofs.}
Clearly we have priv $\Rightarrow$ wpriv, tightly and by an obvious
reduction.  The converse is not true, however: consider the previous
construction in which $M = S \setminus \{x\}$ for a random $x \in S$,
and $\pubaux=\privaux=\emptystring$.  We note that this construction
also serves to separate the priv notion from our notion of
correctness.  (It is $1-(1/|S|)$ correct, but has no priv-security.)

Curiously, the trivial scheme that sets $M=S$, $\pubaux=\privaux=\emptystring$ does seem to be both correct and wpriv-secure (up to the element-wise min-entropy of~$S$).
\tsnote{In general, reducing correctness to wPriv is syntactically possible, but not clear how to connect the success events.  In the one-wayness game, you win by outputing an element of~$S$; but how does this lead to finding an error-inducing query?  Maybe the one-wayness attacker makes no queries, and just outputs a point~$z$.  Then the correctness attacker does what?  Ask some query~$q_z$ related to~$z$ ---remember, queries are not syntactically restricted to set membership!--- and see if the oracle returns the true value $q_z(S)$?  This is pretty complicated... and it's not clear how to do a quality reduction.   }
\tsnote{Likewise the other way: the one-wayness adversary does not get~$S$, and yet needs to provide this to the correctness adversary.}

\todo{We should be able to show...}
\begin{itemize}
\item ss-rep $\Rightarrow$ priv \emph{for set-multiplicity data
    structures} \tsnote{but probably not in general}
\item \{w\}priv $\not\Rightarrow$ ss-rep
\end{itemize}

>>>>

Our semantic-secure definition is simulation-based (see Figure~\ref{fig:privacy-ss}).
In this definition we compare the probabilities with which an attacker $A$ outputs~1
in two experiments: one ``real'' and one ``simulated.''
In the real experiment (ss-rep-1), $A$ outputs a set $S$  and is given the
public information $\pubaux$ that results from running $\Rep(S)$.
\footnote{We do not give $A$ an oracle for issuing queries; 
since $A$ knows the set~$S$, such an oracle would be superfluous.
\jnote{Interestingly,
if we provided a query oracle in the real world and an oracle that returns the correct
answer in the simulated world, then the definition seems to imply
correctness also.}}
In the simulated experiment (ss-rep-0), $A$ outputs $S$ and is given $\pubaux$ output
by a simulator $\Sim$ that is only given ${\sf leak}(S)$ for some (possibly randomized)
function~${\sf leak}$.
For a given function ${\sf leak}$, adversary $A$, and simulator~$\Sim$,
we define the advantage measure
$\AdvPrivSS{\Pi,{\sf leak}}{A,\Sim} \bydef
\left| \Prob{\ExpPrivSSreal{\Pi}{A}=1} -
\Prob{\ExpPrivSSsim{\Pi,{\sf leak}}{A, \Sim}=1} \right|$.
Informally, a scheme $\Pi$ is secure with respect to some leakage function ${\sf leak}$
if for all $A$ there is a simulator $\Sim$ such that
$\AdvPrivSS{\Pi,{\sf leak}}{A,\Sim}$ is small.
Intuitively, this means that the public portion
$\pubaux$ of the representation of a set~$S$ leaks~${\sf leak}(S)$ and nothing more.
\jnote{Need to relate running time of $\Sim$ to running time of~$A$.}
\todo{Introduce OW notion, if we keep it}
\begin{figure}[hbtp]
\centering
\fpage{.6}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpPrivSSreal{\Pi}{A}$}\\
$(S,\st) \getsr A()$ \\
$(\pubaux,\privaux) \getsr \Rep(S)$\\
return $A(\st,\pubaux)$\\
}
%
{
\experimentv{$\ExpPrivSSsim{\Pi, {\sf leak}}{A, \Sim}$}\\
$(S,\st) \getsr A()$\\
$(\st,\pubaux) \getsr \Sim({\sf leak}(S))$ \\
return $A(\st,\pubaux)$\\
}
}
\caption{Experiments for a ``semantic-security'' style privacy
  definition.}
\label{fig:privacy-ss}
\end{figure}

\begin{figure}[hbtp]
\centering
\fpage{.6}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpPrivOW{\setprim,\distr{}{}}{A}$}\\
$S \getsr \distr{}{}$\\
$(\pubaux,\privaux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(\pubaux)$\\
if $z \in S$ then return 1\\
return 0\\
}
{
\oracle{$\TestOracle(q)$}\\
eturn $\Qry(\pubaux,\privaux,q)$
}
}
\caption{Experiments for a ``one-way'' style privacy
  definition.}
\label{fig:privacy-ow}
\end{figure}

@@

\heading{Relationships Among Notions.} \todo{SS$\Rightarrow$OW?
  (Probably not in general, but perhaps for set-multiplicity data
  structures that satisfy certain assumptions on the query set.)
  SS$\not\Rightarrow$ correctness; the converse is already shown by
  the example I gave earlier, i.e. $M=S\setminus\{x\}$ for random $x
  \in S$.}
